#Part 1 - Data preparation

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(vegan)
library(paletteer)
```

```{r}
NRSdata <- read.csv("Updated NRS data for Rstudio .csv")
```

```{r}
NRSdata$Date <- as.Date(NRSdata$Date, tryFormats = c("%d/%m/%Y"))
```

```{r}
NRSdata$Month <- substr(NRSdata$Date, 6,7)
NRSdata$Year <- substr(NRSdata$Date, 1, 4)

NRSdata$Year <- as.numeric(NRSdata$Year)
NRSdata$Month <- as.numeric(NRSdata$Month)

NRSdata <- NRSdata %>%
  mutate(Season = ifelse(Month %in% 9:11, "Sp",
                          ifelse(Month %in% c(12,1,2), "Su",
                                 ifelse(Month %in% 3:5, "Au",
                                        "Wi"))))
NRSdata <- NRSdata %>%
  mutate(Yr2 = ifelse(Month == 12, Year + 1, Year))
NRSdata$Yr2 <- substr(NRSdata$Yr2, 3,4)
NRSdata$SeasonYr <- paste(NRSdata$Season, NRSdata$Yr2)
NRSdata$SeasonYr <- factor(NRSdata$SeasonYr, levels = c("Sp 14", "Su 15", "Au 15", "Wi 15", "Sp 15", "Su 16", "Au 16", "Wi 16", "Sp 16", "Su 17", "Au 17", "Wi 17", "Sp 17", "Su 18", "Au 18", "Wi 18", "Sp 18", "Su 19", "Au 19", "Wi 19", "Sp 19", "Su 20", "Au 20", "Wi 20", "Sp 20", "Su 21", "Au 21", "Wi 21", "Sp 21", "Su 22"))
str(NRSdata)
summary(NRSdata)

NRSdata$Season <- factor(NRSdata$Season, levels = c("Sp", "Su", "Au", "Wi"))

NRSdata$Volume_m3 <- as.numeric(NRSdata$Volume_m3)
NRSdata$Project_name <- factor(NRSdata$Project_name, levels = c("NRS_NSI", "NRS_PH", "NRS_MAI"))
NRSdata$Location <- as.factor(NRSdata$Location)
NRSdata$Gear_depth_m <- as.numeric(NRSdata$Gear_depth_m)
NRSdata$Gear_mesh_um <-as.factor(NRSdata$Gear_mesh_um)
```

```{r}
NRSdata_long <- NRSdata %>%
  pivot_longer(cols = 14:24, names_to = "Species", values_to = "Abundance")#cols = species columns only
```

#Code for subsetting data for each site
newdat <- dat %>%
filter(Location == "name_loc")

NRSdata$Location <- factor(NRSdata$Location, levels = c("North Stradbroke", "Port Hacking", "Maria Island")) 

```{r}
NRSdata_long <- NRSdata_long %>%
  mutate(NewVol = ifelse(Gear_mesh_um == "Bongo-500", Volume_m3/2,
                         Volume_m3))

NRSdata_long <- NRSdata_long %>%
  mutate(conc_per_m3 = Abundance/NewVol) %>%
  mutate(conc_per_100_m3 = conc_per_m3*100)

NRSdata <- NRSdata %>%
  mutate(NewVol = ifelse(Gear_mesh_um == "Bongo-500", Volume_m3/2,
                         Volume_m3))
```

#Joining CTD data

Can use season and season-year code from prior script to make legend - scale_colour_discrete
  
  #Join docs together
  #All_raw_data <- left_join(NRSdata, CTD_data, by=c("Project_name, "Date))
  
  #to remove columns
  #select(c(-Conductivity, -Turbidity, -etc))
  
#removing all tows with no species collected, removing all tows with 'NA' values 
#All_raw_data <- All_raw_data %>%
#filter_at(c(11:22), any_vars(. !=0)) #11:22 is just example - numbers should correspond to species column
#All_raw_data <- na.omit(All_raw_data)

```{r}
CTD_join_data <- CTD_summary %>%
  select(c(1:3, 6, 9, 12, 15, 21))

Project_name <- c("NRS_NSI","NRS_PH", "NRS_MAI")
site_code <- c("NRSNSI", "NRSPHB", "NRSMAI")
df <- data.frame(site_code, Project_name)
CTD_join_data <- left_join(CTD_join_data, df, by="site_code")

summary(CTD_summary)
CTD_join_data$Project_name <- as.factor(CTD_join_data$Project_name)
```
```{r}
Combined_data <- left_join(NRSdata, CTD_join_data, by=c("Project_name", "Date"))

Combined_data <- Combined_data %>%
  select(-mean_DOX, -mean_TURB, -mean_CNDC)

Combined_data_long <- Combined_data %>%
  pivot_longer(cols = 14:24, names_to = "Species", values_to = "Abundance")#cols = species columns only

Combined_data_long <- Combined_data_long %>%
  mutate(conc_per_m3 = Abundance/NewVol) %>%
  mutate(conc_per_100_m3 = conc_per_m3*100)
```

#Part 2 - Temperature-Salinity Plot

```{r}
Combined_data_long$Species <- as.factor(Combined_data_long$Species)
Combined_data_long <- Combined_data_long %>%
  filter(conc_per_100_m3 !=0)
```

testplot <- ggplot(data = Combined_platys, aes(x = mean_Salinity, y = mean_TEMP, group = Species)) +
  geom_point(aes(color = Species, size = species_conc_100), position = "jitter") +
  labs(x = "Mean Salinity (Practical Salinity Units) <30m", y = bquote('Mean Temperature (°c) <30m')) +
  scale_color_paletteer_d("ggsci::default_locuszoom", name = "Taxa") +
  ylim(11.5,27) +
  theme_IRboxplot +
  theme(legend.text = element_text(face = "italic"))
testplot
ggsave(testplot, file = "TSplot.png", bg = "transparent", width = 26, height = 15, units = "cm")

```{r}
testplot <- ggplot(data = Combined_data_long, aes(x = mean_Salinity, y = mean_TEMP, group = Species)) +
  geom_point(aes(color = Species, size = conc_per_100_m3), position = "jitter") +
  labs(x = "Mean Salinity (Practical Salinity Units) <30m", y = bquote('Mean Temperature (°c) <30m')) +
    scale_color_paletteer_d("ggsci::default_locuszoom", name = "Taxa") +
  ylim(11.5,27) +
  theme_IRboxplot +
  theme(legend.text = element_text(face = "italic"))
  
#substitute in log-transformed +1 for conc_per_100_m3

#subsetting data:example syntax

Combined_platys_long <- Combined_data_long %>%
  filter(Species == "P..grandispinis"|Species == "P..fuscus")
```

#Part 3 - Generalised Linear Models and ANOVAs

```{r}
library(mvabund)

Combined_data_clean <- na.omit(Combined_data)
Combined_data_clean <- Combined_data_clean %>%
  filter_at(c(14:24), any_vars(. != 0))

Flathead_spp <- mvabund(Combined_data_clean[, 14:24])

par(mar = c(2, 10, 2, 2)) # adjusts the margins
boxplot(Combined_data_clean[, 14:24], horizontal = TRUE, las = 2, main = "Abundance") 
```
```{r}
meanvar.plot(Flathead_spp) #broken (run in console)
plot(Flathead_spp ~ as.factor(Combined_data_clean$Project_name), cex.axis = 0.8, cex = 0.8)


mod1 <- manyglm(Flathead_spp ~ Combined_data_clean$Project_name, 
                family = "poisson",
                offset = log(Combined_data_clean$NewVol))
plot(mod1)

mod2 <- manyglm(Flathead_spp ~ Combined_data_clean$Project_name, 
                family = "negative_binomial",
                offset = log(Combined_data_clean$NewVol))
plot(mod2)

anova(mod2)
anova(mod2, p.uni = "adjusted")
Anovamod2 <- anova(mod2)

mod3 <- manyglm(Flathead_spp ~ Combined_data_clean$Project_name*Combined_data_clean$Season*Combined_data_clean$Year, 
                family = "negative_binomial",
                offset = log(Combined_data_clean$NewVol))

anova(mod3, p.uni = "adjusted")
```
#Follow-up
```{r}
mod4 <- manyglm(Flathead_spp ~ Combined_data_clean$mean_Salinity + Combined_data_clean$mean_CPHL + Combined_data_clean$mean_TEMP,
family = "negative_binomial",
offset = log(Combined_data_clean$NewVol))

anova(mod4, p.uni = "adjusted")
```



#From 7/10/2022 - run this

```{r}
library(ecoCopula)
library(ggrepel)
library(viridis)
library(ggrepel)

mod3_null <- manyglm(Flathead_spp ~ 1, family="negative_binomial", 
                offset=log(Combined_data_clean$NewVol))
```

```{r}
fish_lv=cord(mod3_null)
# plot it
plot(fish_lv,biplot = TRUE)

Lv_scores <- as.data.frame(fish_lv$scores)
Sp_loadings <- as.data.frame(fish_lv$loadings)
Sp_loadings$Length <- sqrt(Sp_loadings$Factor1^2 + Sp_loadings$Factor2^2) # calculate vector length
Sp_loadings$Species <- colnames(Flathead_spp)   
Sp_loadings_10 <- Sp_loadings %>% slice_max(order_by = Length, n=9) # 10 longest vectors
```
 

```{r}
Sp_loadings_10$SpeciesLabs <- c("P. grandispinis", "A. jugosa", "P. caeruleopunctatus", "P. endrachtensis", "P. bassensis", "P. richardsoni", "S. tuberculata", "P. fuscus", "Ratabulus spp.")
```


 
```{r}
# plot by Season
seasonplot <- ggplot(Combined_data_clean) + 
  geom_point(data=Lv_scores, aes(x=Factor1, y = Factor2, col=Combined_data_clean$Project_name)) + 
  scale_color_viridis(discrete = TRUE, option = "plasma", direction = -1) +
  annotate("segment", x = rep(0,10), xend = Sp_loadings_10$Factor1*3, y = rep(0,10), yend = Sp_loadings_10$Factor2*3, colour = "gray25", size=0.5, alpha=0.6, arrow=arrow())+
geom_text_repel(data=Sp_loadings_10, 
                    aes(x = Factor1*3, y = Factor2*3, label=Species)) +  
  xlab("Latent Variable 1") + ylab("Latent Variable 2")
seasonplot

# Plot by Project_name
#Without sps vectors
ggplot(Combined_data_clean) + geom_point(data=Lv_scores, aes(x=Factor1, y = Factor2, col=Combined_data_clean$Project_name)) + theme_classic() + scale_colour_viridis_d("IMOS NRS") 

#With sps vectors
vectplot <- ggplot(Combined_data_clean) + 
  geom_point(data=Lv_scores, aes(x=Factor1, y = Factor2, color=Combined_data_clean$Project_name, shape = Combined_data_clean$Season), size = 5) + 
  theme_classic() + 
  annotate("segment", x = rep(0,9), xend = Sp_loadings_10$Factor1*3, y = rep(0,9), yend = Sp_loadings_10$Factor2*3, colour = "gray25", size=0.5, alpha=0.6, arrow=arrow()) +
    geom_text_repel(data=Sp_loadings_10, 
                    aes(x = Factor1*3, y = Factor2*3, label=SpeciesLabs, fontface = "italic"), size = 5) +
  xlab("Latent Variable 1") + 
  ylab("Latent Variable 2") +
  scale_color_discrete(name = "IMOS NRS", labels = c("North Stradbroke Island", "Port Hacking", "Maria Island")) +
  scale_shape_discrete(name = "Season") +
 theme(axis.title=element_text(size = 20)) +
    theme(axis.text.y = element_text(size = 20)) +
  theme(axis.text.x = element_text(size = 20)) +
   theme(legend.title = element_text(face = "bold", size = 18)) +
  theme(legend.text = element_text(size = 15)) +
  theme(legend.position = "bottom")
vectplot
ggsave("2025 Manuscript Platy GLM Ordination.pdf", width = 32, height = 20, units = "cm")
```

https://environmentalcomputing.net/statistics/mvabund/

#For mean and SD table:

summary_fishies <- Combiend_data_long %>%
group_bu(Project_name, Species) %>%
summarise(overall_abun = n(),
mean_abun = mean(Abdundance)...


```{r}
install.packages("tinytex")
library(tinytex)
library(vegan)
```



